%
% brownletter_example.tex - an example latex file to illustrate brownletter.cls
%
% Copyright 2003, Nesime Tatbul (tatbul@cs.brown.edu)
%

\documentclass[11pt]{brownletter}

\name{Andrew Mokotoff} % used as signature, if no signature is specified

\signature{\vspace{18pt} Andrew Mokotoff\\Chapter President}

\date{November 27, 2016} % if no date specified, today's date is used 

\subject{Sanctions} % optional subject line

\begin{document}

\begin{letter}{Benjamin A. Seitz\\
               99 Salisbury Street\\ 
               Worcester, MA 01609}

\opening{Dear Brother Benjamin Seitz,}

After reviewing the evidence and the judicial board's investigation we have come to a conclusion. By consensus of the judicial board, we have found you \textbf{not responsible} for Disorderly Conduct. You do not consume alcohol and were not involved in the actions of the other brothers. Since the people you were transporting discretely had alcohol, we have found you \textbf{not responsible} for Underage Drinking/Transportation. 

In place we request that you complete the following items:
\begin{enumerate}
\item You will be required to complete twenty hours of community service before the start of C-Term (January 12, 2017).
\item You will write an apology letter to Holy Cross, the Worcester Polytechnic Institute, and the WPI Hockey Team
\item A fine of \$100 must be payed to Phi Gamma Delta before the start of C-Term (January 12, 2017).
\end{enumerate}

Failure to meet these items and/or any action that reflects poorly on the brotherhood, will subject you to denial of chapter privileges with our national headquarters. By signing below you agree to these terms.

\vspace{0.5cm}

\closing{Sincerely,}



\end{letter}

\end{document}